### 2014-01-15 manuscripts/dpp-msbayes/dpp-msbayes-main.tex
Working on reply and dpp ms.
More edits to dpp ms, and adding Efron (2008) citation to
reply.

Furthermore, the modifications to the model also improve the method's power to
detect random variation in divergence times, reducing the tendency to estimate
clustered divergences
(Figures~\labelcref{figPowerPsiOld4,figPowerPsiProbOld4,figPowerOmegaOld4,figPowerOmegaProbOld4}).
Our results are similar to those of \citet{Oaks2012} in that we also find
the \msb model to infer strong support for clustered divergences when
divergences are random over quite broad timescales
(Figures~\labelcref{figPowerPsiOld4,figPowerPsiProbOld4,figPowerOmegaOld4,figPowerOmegaProbOld4}).
Our results expand on this by showing that this behavior is consistent
across a range of conditions underlying the data.
The new method \dppmsbayes has greater power to detect random temporal variation in
divergences, is less prone to spurious inference of clustered divergence
models, and much less likely to incorrectly infer such models with strong
support
(Figures~\labelcref{figPowerPsiOld4,figPowerPsiProbOld4,figPowerOmegaOld4,figPowerOmegaProbOld4}).

@@

While our modifications improve the behavior of the model, we urge caution when
using the method and interpreting its results.
The method attempts to approximate the posterior of a very parameter-rich model
using relatively little information from the data.
For example, when applied to the dataset of 22 taxon pairs from the Philippines
\citet{Oaks2012} the model can have as many as 604--625 free parameters
(depending on \divTimeNum), and samples over 1002 unordered divergence models.
Even under the simplest possible model allowed under our new implementation,
the model still has 471--492 free parameters.
Furthermore, the coalescent and mutational models specified by these parameters
predict a large amount of variation in possible datasets even when the
parameter values are known.
Sampling over hundreds of parameters and more than a thousand models is a
difficult inference problem, especially when only using a small number of
summary statistics calculated from the sequence alignments of each taxon pair.
The population-genetic summary statistics used by our method contain little
information about many of the free parameters in the model.
Thus, we expect the improved method will still be sensitive to priors, and the
power, while improved, may still be low.
While we see much less prior sensitivity under the new model compared to those
observed by \citet{Oaks2012}, we still some evidence of such sensitivity when
comparing the results of the empirical data analyzed under a diffuse
(\empModelDPP) and informative (\empModelDPPInform) divergence-time prior
(Figure~\ref{figPhilippines} C versus D).
The fact that the posterior shifts toward the prior under the informative prior
suggests that the shift away from the prior toward fewer divergence events
under the diffuse prior might be still be caused by small marginal likelihoods
of models with more divergence-time parameters (Figure~\ref{figPhilippines}).

Nonetheless, it is reassuring to see a large amount of posterior uncertainty
when the new implementation is applied to the empirical datasets
(Figure~\labelcref{figPhilippines,figNegrosPanay}).
Applications of the \msb model often result in strong posterior support for
estimated scenarios
\citep{Barber2010,Bell2012,Carnaval2009,Chan2011,Hickerson2006,Leache2007,Plouviez2009,Stone2012,Voje2009,Oaks2012},
as we found here (Figure~\ref{figPhilippines}).
Given the richness of the model, the variance of the processes being modeled,
and the relatively small amount of information in the summary statistics
calculated from the sequence data, we do not expect to find strong posterior
support for any scenario.
Based on results of the empirical and power analyses
(Figures~\labelcref{figPowerPsiProbOld4,figPowerOmegaProbOld4,figPhilippines,figNegrosPanay})
the new implementation more accurately reflects posterior uncertainty and
avoids spurious support for biogeographic scenarios.

We also urge caution when applying \dppmsbayes due to the fact that ABC methods
in general are known to be biased for model choice \citep{Robert2011}.
As recommended by \citet{Oaks2012}, any results from the method should be
accompanied by assessments of prior sensitivity and power.
We encourage investigators to view this method as a means of exploring their
data rather than a rigorous means of evaluating hypotheses.

>>>>

The modifications to the model also improve the method's power to detect random
variation in divergence times, reducing the tendency to estimate clustered
divergences
(Figures~\labelcref{figPowerPsiOld4,figPowerPsiProbOld4,figPowerOmegaOld4,figPowerOmegaProbOld4}).
Our results are similar to those of \citet{Oaks2012} in that we also find
the \msb model to infer strong support for clustered divergences when
divergences are random over quite broad timescales
(Figures~\labelcref{figPowerPsiOld4,figPowerPsiProbOld4,figPowerOmegaOld4,figPowerOmegaProbOld4}).
Our results expand on this by showing that this behavior is consistent
across a range of conditions underlying the data.
The new method \dppmsbayes has greater power to detect random temporal variation in
divergences, is less prone to spurious inference of clustered divergence
models, and much less likely to incorrectly infer such models with strong
support
(Figures~\labelcref{figPowerPsiOld4,figPowerPsiProbOld4,figPowerOmegaOld4,figPowerOmegaProbOld4}).

@@

While our modifications improve the behavior of the model, we urge caution when
using the method and interpreting its results.
The method attempts to approximate the posterior of a very parameter-rich model
using relatively little information from the data.
For example, when applied to the dataset of 22 taxon pairs from the Philippines
\citep{Oaks2012} the model can have as many as 604--625 free parameters
(depending on \divTimeNum), and samples over 1002 unordered divergence models.
Even under the simplest possible model allowed under our new implementation,
the model still has 471--492 free parameters.
Furthermore, the stochastic coalescent and mutational processes being modeled
predict a large amount of variation in possible datasets even when the
parameter values are known.
The richness and stochastic nature of the model makes for a difficult inference
problem, especially when using a small number of summary statistics calculated
from the sequence alignments of each taxon pair.
The population-genetic summary statistics used by our method contain little
information about many of the free parameters in the model.
Thus, we expect the improved method will still be sensitive to priors, and the
power, while improved, may still be low.
While we see much less prior sensitivity under the new model compared to those
observed by \citet{Oaks2012}, we still see an effect when comparing the results
of the empirical data analyzed under a diffuse (\empModelDPP) and informative
(\empModelDPPInform) divergence-time prior (Figure~\ref{figPhilippines} C
versus D).
The fact that the posterior shifts toward the prior under the informative prior
suggests that the shift away from the prior toward fewer divergence events
under the diffuse prior might still be caused by small marginal likelihoods
of models with more divergence-time parameters (Figure~\ref{figPhilippines}).

Nonetheless, it is reassuring to see a large amount of posterior uncertainty
when the new implementation is applied to the empirical datasets
(Figure~\labelcref{figPhilippines,figNegrosPanay}).
Applications of the \msb model often result in strong posterior support for
estimated scenarios
\citep{Barber2010,Bell2012,Carnaval2009,Chan2011,Hickerson2006,Leache2007,Plouviez2009,Stone2012,Voje2009,Oaks2012},
as we found here (Figure~\ref{figPhilippines}).
Given the richness of the model, the variance of the processes being modeled,
and the relatively small amount of information in the summary statistics
calculated from the sequence data, we do not expect to find strong posterior
support for any scenario.
Based on results of the empirical and power analyses
(Figures~\labelcref{figPowerPsiProbOld4,figPowerOmegaProbOld4,figPhilippines,figNegrosPanay}),
the new implementation more accurately reflects posterior uncertainty and
avoids spurious support for biogeographic scenarios.

We also urge caution when using \dppmsbayes due to the fact that ABC methods
in general are known to be biased for model choice \citep{Robert2011}.
As recommended by \citet{Oaks2012}, any results from the method should be
accompanied by assessments of prior sensitivity and power.
We encourage investigators to view this method as a means of exploring their
data rather than a rigorous means of evaluating hypotheses.

### 2014-01-15 manuscripts/reply/reply-main.tex
Working on reply and dpp ms.
More edits to dpp ms, and adding Efron (2008) citation to
reply.

This complicates the meaning of model posterior probabilities when Bayes' rule
is violated by informing priors with the same data to be analyzed.
For empirical Bayesian parameter estimation, the objective is that by giving the
data more weight relative to the prior, the posterior distribution will be
peaked near the true value(s) of the model's parameter(s).
There is no such justification for empirical Bayesian model choice, because
there are no true values for the model probabilities being estimated.
By using the data twice, we fail to account for prior uncertainty and mislead
our posterior beliefs in the models being compared; we will be over confident
in some models and under confident in others.

>>>>

This complicates the meaning of model posterior probabilities when Bayes' rule
is violated by informing priors with the same data to be analyzed.
For empirical Bayesian parameter estimation, the objective is that by giving the
data more weight relative to the prior, the posterior distribution will be
peaked near the true value(s) of the model's parameter(s).
There is no such justification for empirical Bayesian model choice, because
there are no true values for the model probabilities being estimated.
By using the data twice, we fail to account for prior uncertainty and mislead
our posterior beliefs in the models being compared; we will be over confident
in some models and under confident in others.
Nonetheless, empirical Bayesian model choice does perform well for some
inference problems.
Particularly, in cases where large aggregate data sets are used for many
parallel model-choice problems simultaneously, pooling information to inform
priors can lead to favorable group-wise frequentist coverage across tests
\citep{Efron2008}.
